European or American? A re-examination of the transatlantic influence over the IMF

### 2025-10-04 manuscript/manuscript.qmd
Add tests for manuscript (#88)
* Initial plan

* Add comprehensive test suite for manuscript.qmd

Co-authored-by: kv9898 <105025148+kv9898@users.noreply.github.com>

* Update README to document new manuscript test

Co-authored-by: kv9898 <105025148+kv9898@users.noreply.github.com>

* change expected length to 400

* remove non-dependencies

* Fix that part that checks loading

* Remove final parts

* Add helper for extracting r chunks

* Add script for testing R chunks in manuscript.qmd by claude

* Refactor wd and reformat

* bind lines together

* manuscript: fix 2nd chunk name

* improved s

```{r}
#| label: tbl-summary
#| tbl-cap: Summary Statistics of Key Variables (1980–2010)
#| tbl-pos: H
library(modelsummary)
dsummary(
  (`IMF loan to GDP ratio (%)` = imfloannew100) +
    (`IMF participation rate` = imf_p) +
    (`IMF loan approval` = imf5a) +
    (`Number of IMF conditions` = tc) +
    (`USA Influence` = us) +
    (`EUP Influence` = eu) +
    (`IMF Staff (log)` = shstaffl) +
    (`IMF Quota (log)` = `shquotal`) +
    (`GDP (log)` = lnrgdpnew) +
    (`GDPpc (thousands USD)` = rgdpchnew) +
    (`GDPpc growth (%)` = growth1new) +
    (`Reserves (months of imports)` = reserv1) +
    (OECD = oecd1) ~ 
    Mean + SD + Min + (Q1 = P25) + Median + (Q3 = P75) + Max + N,
  data = dta
) |> tinytable::theme_latex(resize_width = 1, resize_direction = "down")
```

>>>>

```{r}
#| label: tbl-summary
#| tbl-cap: Summary Statistics of Key Variables (1980–2010)
#| tbl-pos: H
library(modelsummary)
dsummary(
  (`IMF loan to GDP ratio (%)` = imfloannew100) +
    (`IMF participation rate` = imf_p) +
    (`IMF loan approval` = imf5a) +
    (`Number of IMF conditions` = tc) +
    (`USA Influence` = us) +
    (`EUP Influence` = eu) +
    (`IMF Staff (log)` = shstaffl) +
    (`IMF Quota (log)` = `shquotal`) +
    (`GDP (log)` = lnrgdpnew) +
    (`GDPpc (thousands USD)` = rgdpchnew) +
    (`GDPpc growth (%)` = growth1new) +
    (`Reserves (months of imports)` = reserv1) +
    (OECD = oecd1) ~ 
    Mean + SD + Min + (Q1 = P25) + Median + (Q3 = P75) + Max + N,
  output = "latex",
  data = dta
) |> tinytable::theme_latex(resize_width = 1, resize_direction = "down")
```
